Statement-level AST-based Clone Detection in Java using Resolved Symbols

### 2019-11-07 benevol/paper.tex
Updates from Overleaf

We find that 167,913 clones are found when contextual information is not considered, whereas 149,569 clones are found when it is considered. We manually analyse a sample of 50 clones that are not found when considering contextual information. We found that these clones are indeed hard to refactor because they describe different functional operations and can thus not be extracted to a new method. Also, most often they were not relevant because, based on our judgement, refactoring would not improve the code design. Often, different methods were called or variables of different types were used.

@@

We define three aspects of source code as the contextual information:
\begin{itemize}
    \item The type of variable references.
    \item The location of method references.
    \item The location of type references.
\end{itemize}
When these references have the same name but point to different locations, clones may not be easily refactorable. Our results show that most such clones are not relevant for refactoring. This accounts for about 11\% of clones. This comes however with a performance trade-off: detecting clones with contextual information took 13 times longer than when not taking contextual information into account (1.6min vs 20.8min).

>>>>

We find that 167,913 clones are found when contextual information is not considered, whereas 149,569 clones are found when it is considered. We manually analyse a sample of 50 clones that are not found when considering contextual information. We find that these clones are indeed hard to refactor because they describe different functional operations and can thus not be extracted to a new method. Also, most often they were not relevant because, based on our judgement, refactoring would not improve the code design. Often, different methods were called or variables of different types were used.

@@

We define three aspects of source code as the contextual information:  a) the type of variable references; b) the location of method references; and c) the location of type references. When these references have the same name but point to different locations, clones may not be easily refactorable. Our results show that most such clones are not relevant for refactoring. This accounts for about 11\% of clones. This comes however with a performance trade-off: detecting clones with contextual information took 13 times longer than when not taking contextual information into account (1.6min vs 20.8min).
